On the Cold Deformation Behavior of Two Phase TiAl Alloy with and without Void Defects

### 2018-10-02 draft/ed3.tex
add subsect

% Full title of the paper (Capitalized)
% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
\Title{On the Cold Deformation Behaviour of Two Phase TiAl Alloy with and without Void Defects}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\bibliography{ref/VIOLET-ref.bib}

\section{Introduction}
TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{vu2013}. Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}. Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator.

@@

MD simulations has reveals that existence of voids alone may contribute to strain hardening because theyare barriers to dislocation movement \cite{Xiong2015}

@@

\cite{}
$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}. Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures. The initial dimension of simulation cell is  $L_x = $ nm, $L_y = $ nm, $L_z = $ nm, and each model contains about 4.6 million atoms. The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains. Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model. The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig. \cite{}. The intergranular spherical void was at the center of the simulation cell, as shown in Fig. \cite{}.

@@

\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{"img/dis-void"}
	\caption{Dislocation around void}
	\label{fig:dis-void}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{"img/orowan"}
	\caption{orowan}
	\label{fig:dis-void}
\end{figure}

A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}. A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}. If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to

@@

According to Schmid's law:
	$$\tau = \sigma*m$$
where m is the Schmid factor :
	$$ m = cos(\phi)cos(\lambda)$$
	%\subsection{The influence of void on strength of TiAl alloy}
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame2}
%		\caption{stress-$\sigma$=0}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame150}
%		\caption{stress-$\sigma$=0.15}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame160}
%		\caption{stress-$\sigma$=0.16}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame170}
%		\caption{stress-$\sigma$=0.17}
%		\label{ }
%	\end{figure}
%	
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame180}
%		\caption{stress-$\sigma$=0.18}
%		\label{ }
%	\end{figure}
%The location of void affects strength of material. Comparing with the model with integranular void, the model with %intergranular voids is weaker. atomic stress is calculated 
%	
%	
%	
%	
%	
%	% \begin{figure}[ht]
%	% 	\centering
%	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
%	% 	\caption{stress-strain curve}
%	% 	\label{fig:ia_line}
%	% \end{figure}
%	% 
%	% \begin{figure}[ht]
%	% 	\centering
%	% 	\includegraphics[width=0.7\linewidth]{img/agline}
%	% 	\caption{stress-strain curve}
%	% 	\label{fig:ag_line}
%	% \end{figure}
%	
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/1stdiv}
%		\label{fig:surf}
%		\caption{stress-strain curve}
%	\end{figure}
%	
%	
%	\section{Conclusion}
%	%\bibliographystyle{elsarticle-num.bst}
%

>>>>

% Full title of the paper (Capitalized)
% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
\Title{On the Cold Deformation Behavior of Two Phase TiAl Alloy with and without Void Defects}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\section{Introduction}
TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{vu2013}. Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}. Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator.

@@

@@

$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}. Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures. The initial dimension of simulation cell is  $L_x = $ nm, $L_y = $ nm, $L_z = $ nm, and each model contains about 4.6 million atoms. The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains. Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model. The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig. \cite{}. The intergranular spherical void was at the center of the simulation cell, as shown in Fig. \cite{}.

@@

\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}. A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}. If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to

@@

According to Schmid's law:
	$$\tau = \sigma*m$$
where m is the Schmid factor :
	$$ m = cos(\phi)cos(\lambda)$$
	%\subsection{The influence of void on strength of TiAl alloy}
	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.7\linewidth]{img/frame2}
		\caption{stress-$\sigma$=0}
		\label{ }
	\end{figure}

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.7\linewidth]{img/frame150}
		\caption{stress-$\sigma$=0.15}
		\label{ }
	\end{figure}

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.7\linewidth]{img/frame160}
		\caption{stress-$\sigma$=0.16}
		\label{ }
	\end{figure}

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.7\linewidth]{img/frame170}
		\caption{stress-$\sigma$=0.17}
		\label{ }
	\end{figure}

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.7\linewidth]{img/frame180}
		\caption{stress-$\sigma$=0.18}
		\label{ }
	\end{figure}
The location of void affects strength of material. Comparing with the model with integranular void, the model with intergranular voids is weaker. atomic stress is calculated

	% \begin{figure}[ht]
	% 	\centering
	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
	% 	\caption{stress-strain curve}
	% 	\label{fig:ia_line}
	% \end{figure}
	% 
	% \begin{figure}[ht]
	% 	\centering
	% 	\includegraphics[width=0.7\linewidth]{img/agline}
	% 	\caption{stress-strain curve}
	% 	\label{fig:ag_line}
	% \end{figure}

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.7\linewidth]{img/1stdiv}
		\label{fig:surf}
		\caption{stress-strain curve}
	\end{figure}

	\section{Conclusion}
	%\bibliographystyle{elsarticle-num.bst}

	\bibliography{ref/VIOLET-ref}
